---
title: "Reproduce output of a paper"
author: "ziweil8"
date: "2018-09-03"
output: workflowr::wflow_html
---
***
## preprocess data 
***

### download data 

Website of sra data[link](https://www.ncbi.nlm.nih.gov/sra/?term=SRP049743)
```{r eval=FALSE}
module load SRA-Toolkit/2.8.2-1-centos_linux64
prefetch -v SRRXXX 
```

the sra data path:/vlsci/SG0010/ziwei/ncbi/public/sra

### Convert sra to fastq

```{r eval=FALSE}
module load SRA-Toolkit/2.8.2-1-centos_linux64 
fastq-dump --split-files SRRXXX.sra 
```

### Move fastq to another path

```{r eval=FALSE}
mv *.fastq/vlsci/SG0010/shared/shared_data/external_public/Russ_2017/raw/fastq
```

### Download fasta

```{r eval=FALSE}
wget ftp://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/000/001/635/GCF_000001635.26_GRCm38.p6/GCF_000001635.26_GRCm38.p6_genomic.fna.gz 

gunzip GCF_000001635.26_GRCm38.p6_genomic.fna.gz
```

the fasta data path:/vlsci/SG0010/shared/shared_data/external_public/Russ_2017/raw/fasta

### build index

```{r eval=FALSE}
bowtie2-build refseq/*.file mm10_index/mm10_index 
```

***
## Mapping
***

### create scirpt

create script with the help of Job script generator for SLURM[https://www.melbournebioinformatics.org.au/jobscript-generator/]
details about some parameters
Job Type:SMP
CPU Cores:12
Memory in Gigabytes:100
hours:23
Modules: Bowtie2/2.3.2-vlsci_intel-2015.08.25

```{r eval=FALSE}
module load Bowtie2/2.3.2-vlsci_intel-2015.08.25
bowtie2 [options]* -x <bt2-idx> {-1 <m1> -2 <m2> | -U <r> | --interleaved <i>} -S [<sam>]
```

for example

```{r eval=FALSE}
bowtie2 -x raw/fasta/index/mm10 -U raw/fastq/SRR1772989_1.fastq  -S output/SRR1772989_Chip-seq.sam   
```

### new a sbatch file

```{r eval=FALSE}
vi filename.sbatch
```

cope all content of script to sbatch file and then press Esc (for exiting insertion statement)

and then save and exit sbatch file

```{r eval=FALSE}
:wq ftp://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/000/001/635/GCF_000001635.26_GRCm38.p6/GCF_000001635.26_GRCm38.p6_genomic.fna.gz
```

###submit sbatch file

```{r eval=FALSE}
sbatch filenam.sbatch
```

### view waiting statement

```{r eval=FALSE}
showq -u ziwei
or 
squeue -u ziwei
```

### path of mapping output

```{r eval=FALSE}
/vlsci/SG0010/shared/shared_data/external_public/Russ_2017/output/sam
```

***
## sam to bam
***

```{r eval=FALSE}
module load SAMtools/1.5-vlsci_intel-2015.08.25-HTSlib-1.5
samtools view -S -b sample.sam > sample.bam
```

### Filter reads with low alignment quality 10

```{r eval=FALSE}
samtools view -b -q 10 output/bam/SRR1772989.bam > output/bam/filteredbam/SRR1772989.qfiltered10.bam
```

***
## bam to hdf5
***

### Index filtered bam files

```{r eval=FALSE}
samtools sort -o sorted.bam initial.bam
samtools index sorted.bam
```

### convert

```{r eval=FALSE}
python load_bam_5prime_ends.py --assembly hg19 /SRR1772989sorted.fwd /SRR1772989sorted.rev /sortedbam/SRR1772989sorted.bam
```
