---
title: "Week 1 Workflow"
output: html_document
---
***

##Libraries
```{r message=FALSE, warning=FALSE, include=TRUE, paged.print=FALSE}
library(tidyverse)
library(tidytext)
library(gutenbergr)
library(glmnet)
library(tm)
library(RColorBrewer)
require(vcd)
```


***
## Data 


#### All The Federalist Papers can be found on gutenberg

```{r message=FALSE, warning=FALSE, paged.print=FALSE}
papers <- gutenberg_download(1404)
head(papers, n = 3)
```



#### Divide each paper up into sentences 

Firstly collapsing all the lines together and splitting them by ".","!" and "?"
```{r}
papers_sentences <- pull(papers, text) %>% 
  str_c(collapse = " ") %>%
  str_split(pattern = "\\.|\\?|\\!") %>%
  unlist() %>%
  tibble(text = .) %>%
  mutate(sentence = row_number())
```



#### Assign each of the 85 papers to the 3 authors and a group unknown papers

```{r}
hamilton <- c(1, 6:9, 11:13, 15:17, 21:36, 59:61, 65:85)
madison <- c(10, 14, 18:20, 37:48)
jay <- c(2:5, 64)
unknown <- c(49:58, 62:63)
papers_words <- papers_sentences %>% #indicate the start of a paper
  mutate(no = cumsum(str_detect(text, regex("FEDERALIST No",
                                            ignore_case = TRUE)))) %>%
  unnest_tokens(word, text) %>%
  mutate(author = case_when(no %in% hamilton ~ "hamilton",
                            no %in% madison ~ "madison",
                            no %in% jay ~ "jay",
                            no %in% unknown ~ "unknown"),
         id = no)
```



#### Exclude Jay

```{r}
papers_words <- papers_words %>%
  filter(author != "jay")
```



#### Tokenize the text

```{r}
papers_words <- papers_sentences %>% #indicate the start of a paper
  mutate(no = cumsum(str_detect(text, regex("FEDERALIST No",
                                            ignore_case = TRUE)))) %>%
  unnest_tokens(word, text) %>%
  mutate(author = case_when(no %in% hamilton ~ "hamilton",
                            no %in% madison ~ "madison",
                            no %in% jay ~ "jay",
                            no %in% unknown ~ "unknown"),
         count = 1) %>% 
  group_by(sentence) %>% 
  filter(sum(count)>=15)  ##filtering out the sentences which length is less than 15 words
```



#### Generate the term-frequency matrix (also named doucument term matrix)

Documents as the rows, terms/words as the columns, frequency of the term in the document as the entries.
```{r}
papers_dtm <- papers_words %>%
  count(no, word, sort = TRUE) %>% 
  cast_dtm(no, word, n)

ham_dtm <- papers_words %>%
  filter(author == "hamilton") %>%
  count(no, word, sort = TRUE) %>% 
  mutate(author="Hamilton") %>% 
  cast_dtm(no, word, n)

mad_dtm <- papers_words %>%
  filter(author == "madison") %>%
  count(no, word, sort = TRUE) %>% 
  mutate(author="Madison") %>% 
  cast_dtm(no, word, n)

unk_dtm <- papers_words %>%
  filter(author == "unknown") %>%
  count(no, word, sort = TRUE) %>% 
  mutate(author="Unknown") %>% 
  cast_dtm(no, word, n)
```



#### Just a quick look of hamilton dtm

```{r}
inspect(ham_dtm[1:5, 1:5])
```



#### dylpr package requires data frame

```{r}
ham_data<-data.frame(as.matrix(ham_dtm))
mad_data<-data.frame(as.matrix(mad_dtm))
unk_data<-data.frame(as.matrix(unk_dtm))
```


***

## Statistics


### whether the length of sentences can be regard as a variable for discrimination


#### Compute the lengths in words of the sentences
```{r}
ham_ls<- papers_words%>% 
  filter(author=="hamilton") %>% 
  group_by(sentence) %>% 
  summarise(length=sum(count))

mad_ls<- papers_words%>% 
  filter(author=="madison") %>% 
  group_by(sentence) %>% 
  summarise(length=sum(count))
```



#### Compute mean and sd 

```{r}
ham_ls %>% 
  summarise(mean=mean(length),sd=sd(length))
mad_ls %>% 
  summarise(mean=mean(length),sd=sd(length))
```



### Which words do they use the most ?


#### Counts of words by author 

```{r}
cs.madison  <- colSums(as.matrix(mad_dtm))       
cs.hamilton <- colSums(as.matrix(ham_dtm))
Counts <- bind_rows(                                
  data_frame(author="Madison",  word=names(cs.madison),  count=cs.madison),
  data_frame(author="Hamilton", word=names(cs.hamilton), count=cs.hamilton))
Counts
```



#### Compute the each word frequency per 1K words
```{r}
M<-data_frame(author="Madison",  word=names(cs.madison),  count=cs.madison)
M <- M %>% 
  mutate( Madison = 1000*count / sum(count)) %>% 
  select(word,Madison)
H<-data_frame(author="Hamilton", word=names(cs.hamilton), count=cs.hamilton)
H <- H %>% 
  mutate( Hamilton = 1000*count / sum(count)) %>% 
  select(word,Hamilton) 
HM<-left_join(H,M,by="word")

HM
```



#### log-odds is more straightforword

```{r}
HM %>% 
  mutate(log_ratio = log2( Hamilton / Madison)) %>% 
  filter(Madison > 1.5 | Hamilton > 1.5) %>% 
  mutate(word = reorder(word, log_ratio)) %>%
  ggplot(aes(word,log_ratio)) +geom_col() + coord_flip() 

```



### which words can show the writing differences between the two authors？


#### To compare some typical words suggested by predecessors

```{r}
Typ_mad<-mad_data/rowSums(mad_data)
Typ_mad<-Typ_mad %>% 
  select(by,from,to,war,tax,upon)

Typ_ham<- ham_data/rowSums(ham_data)
Typ_ham<-Typ_ham %>% 
  select(by,from,to,war,tax,upon)

Typ_joint<-rbind(data.frame(author="hamilton",count=Typ_ham)
                    ,data.frame(author="madison",count=Typ_mad))
colnames(Typ_joint)<-c("author","by", "from", "to", "war", "tax", "upon")

par(mfrow=c(2,3))
aut <- c("hamilton", "madison")
for (w in c("by", "from", "to", "war", "tax", "upon")) {
  boxplot(1000 * Typ_joint[,w] ~ Typ_joint$author, subset = Typ_joint$author %in% aut,
          ylab="Frequency / 1K Words", main=w)
}
```

### Modelling word occurrence


#### Reload the federalist papers text

```{r}
load("FederalistPapers.sav")
federalist <- FederalistPapers %>% 
  filter(text != "") %>% 
  mutate(paper_id=1:85)
```

#### First segment the texts into blocks of about 200 words

```{r}
block_size <- 200
paper_id <- integer()
block_text <- list()
nblock <- 0

for (i in seq_len(nrow(federalist))) {
  # convert the text to a 'String' object to annote it
  s <- NLP::as.String(federalist$text[[i]])
  
  # find the word boundaries
  spans <- NLP::wordpunct_tokenizer(s)
  nword <- length(spans)
  
  # form blocks of 'block_size' words
  end <- 0
  while (end < nword) {
    # find the block boundaries
    start <- end + 1
    end <- min(start + block_size, nword)
    block_span <- Span(spans[start]$start, spans[end]$end)
    
    # store the block in the 'block_text' array
    nblock <- nblock + 1
    block_text[[nblock]] <- as.character(s[block_span])
    paper_id[[nblock]] <- i
  }
}

block <- data_frame(block_id = seq_len(nblock), paper_id = paper_id,
                    text = block_text)
dtm_block <- DocumentTermMatrix(VCorpus(VectorSource(block$text)),
                                control=list(removePunctuation = TRUE))
dtm_block <- sparseMatrix(dtm_block$i, dtm_block$j, x = dtm_block$v,
                          dim=dim(dtm_block), dimnames=dimnames(dtm_block))
```

#### To select a set of words

```{r}
words <- data.frame("may")
words <- words%>% 
  mutate_if(is.factor, as.character) 
names(words)<-"word"
```

#### fit a poisson model for the word by poisson and negtive binomial model.

```{r}
h <- (block %>% left_join(federalist, by="paper_id")
      %>% filter(author == "HAMILTON"))$block_id
x <- dtm_block[h,]

do(words%>% group_by(word), { # for each word:
  # fit a poisson model for the word with parameters estimated by 'Ml'
  y <- table(x[,.$word])
  fit_poisson <- goodfit(y, type="poisson",method = "ML")
  summary(fit_poisson)
  plot(fit_poisson,scale="raw",type="standing")
  lamda1<-data.frame(unlist(fit_poisson$par))
  lamda1
  })
```

```{r}
do(words%>% group_by(word), { # for each word:
  # fit a negative binomial model for the word when it shows a lack of fit of poisson distribution
  y <- x[,.$word]
  fit_nbinomial <- goodfit(y, type="nbinomial")
  summary(fit_nbinomial)
  plot(fit_nbinomial,scale="raw",type="standing")
  lamda2<-data.frame(unlist(fit_nbinomial$par))
  lamda2})
```
